Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-19 demystify.tex
updates

Many students lament that they have a good profile, but still got no interviews or rejected, and that the process seems random.  However, while it is true that the process is not perfect, it is not random.  The short answer is that you do not "fit" the program or the prof.  Why?

Many possible reasons!  Other than not having a strong profile (e.g., research potential, GPA, LoRs, SOP, poor interviews), here are some other reasons.

>>>>

Many students lament that they get no interviews or are rejected (with strong profiles) and that the process seems random.  However, while it is true that the process is not perfect, it is not random.
There are many possible reasons!  Other than not having a strong profile (e.g., research potential, GPA, LoRs, SOP, poor interviews), here are some other reasons.
